Where Do Population III Stars Form?

### 2019-05-08 paper.tex
Making adjustments discussed on 05/08/19.

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}
\usepackage{hyperref}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor can affect the column density of \hh{}, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction. The total number of \hh{} molecules within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$ with $f_{c} = 10^{-2}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}
For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, Figure \ref{fig:H2_column_mass} shows the \hh{} column density as a function of halo mass. Here, the shielding factor is simply $f = 10^{\rm x} / f_{\rm H2}$, and is multiplied to the column density, effectively adjusting the \hh{} fraction within the halo. As the shielding factor increases, the column density can effectively increase by an order of magnitude. The effect of the shielding factor on the column density of \hh{} within a halo is critical in understanding how LW feedback might affect these halos. (More needs to be said here. I'd like to make it more clear about why the shielding factor changes, one way or the other, and the effects of that change. I don't think the plot shows exactly what we want.)

\begin{figure}
	\includegraphics[width=\columnwidth]{images/H2_column_mass.pdf}
    \caption{\hh{} column density versus halo mass for varying shielding factors. At f$_{\rm H2}$ = $10^{-4}$, the shielding factor is equal to one and thus acts as the case where shielding is not applied to the halo.}
    \label{fig:H2_column_mass}
\end{figure}
%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles.

@@

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by an x, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at 10$^{5.9}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to 10$^{6.6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $10^{8.5} M_{\odot}$, a total stellar mass of $10^{6.5} M_{\odot}$, and has a peak Pop III SFR of $10^{-3.5} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $10^{-1.3}$ at $\approx$ 500 Myr. This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.9 and 84.1 percentiles. The right hand side shows the percentage of halos that fall below the M01 mass threshold as a function of redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $z$ = 11.5, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}

@@

At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star. The red line shows the median number of Pop III stars for each halo mass bin. At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$. We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}. The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-3}$ Myr. The red line indicates the median spread in creation times for each halo mass bin. There are two groups within this plot. The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about $10^{-1}$ Myr. The second group contains halos that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr. The second group represents typically larger mass halos that have acquired older Pop III stars by the end of the simulation through their long merger history. These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in Figure \ref{fig:final_redshift_Np3_mass}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.pdf}
    \caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass. A median number of four Pop III stars form in a single halo, with some forming as many as 16 Pop III stars.}
    \label{fig:totnump3_halomass_sidehist}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
    \caption{Total number of Pop III stars in all halos versus halo mass at the end of the simulation, at $z = 9$. The red line indicates the median number of Pop III stars in each halo mass bin.}
    \label{fig:final_redshift_Np3_mass}
\end{figure}

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{caption}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor can affect the column density of \hh{}, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction. The total number of \hh{} molecules within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$ with $f_{c} = 10^{-2}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}
For $z = 15$ and $\rm{H}_{0} = 70 \rm{km} \rm{s}^{-1} \rm{Mpc}^{-1}$, ... 
%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. By the end of the simulation, over 10\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

@@

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by an x, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at $7.7 \times 10^{5}$ M$_{\odot}$ until $z$ = 11.5, at which point, the mean halo mass rises to $3.7 \times 10^{6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $3.6 \times 10^{8} M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4} M_{\odot} yr^{-1}$ at $\approx$ 250 Myr and a peak metal enriched SFR of $5.4 \ times 10^{-2}$ at $\approx$ 500 Myr. This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus time. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.9 and 84.1 percentiles. The right hand side shows the percentage of halos that fall below the M01 mass threshold as a function of redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $\approx$ 380 Myr, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}

@@

At the end of the simulation, Figure \ref{fig:final_redshift_Np3_mass} shows the distribution of the number of Pop III stars per halo for a given halo mass, for all halos in the simulation that host either a living or a remnant Pop III star. The red line shows the median number of Pop III stars for each halo mass bin. At low masses, the number of Pop III stars per halo sits around 2 Pop III stars, and quickly rises once the halo mass reaches $10^{7} M_{\odot}$. We can also look at the spread in creation times of these Pop III stars per halo, shown in Figure \ref{fig:p3spread_mass}. The halos that have a zero spread in their Pop III creation time, meaning the Pop III stars formed at the same time, lie at $10^{-2}$ Myr. The red line indicates the median spread in creation times for each halo mass bin. There are two groups within this plot. The first group contains halos that form their Pop III stars in a spread of < 10 Myr, with a median spread of about $10^{-1}$ Myr. The second group contains halos that form their Pop III stars in a spread of > 10 Myr, with a median spread of about 100 Myr. The second group represents typically larger mass halos that have acquired older Pop III stars by the end of the simulation through their long merger history. These halos have acquired these Pop III stars from outside halos, accounting for the large spread in Pop III creation time as well as the increased number of Pop III stars, as seen in Figure \ref{fig:final_redshift_Np3_mass}.

@@

\begin{figure*}
	\centering
	\begin{subfigure}{.5\textwidth}
  		\centering
  		\includegraphics[width=\columnwidth]{images/totnump3_halomass_sidehist.pdf}
  		\caption{Total number of Pop III stars in halos hosting new Pop III stars versus halo mass at the instance of star formation.}
  		\label{fig:totnump3_halomass_sidehist}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
  		\centering
  		\includegraphics[width=\columnwidth]{images/final_redshift_Np3_mass.pdf}
  		\caption{Total number of Pop III stars in all halos versus halo mass at the end of the simulation, at $z \approx 9$.}
  		\label{fig:final_redshift_Np3_mass}
	\end{subfigure}
	\caption{The number of Pop III stars per halo versus halo mass at the instance of Pop III star formation and the final redshift. On the left, a Pop III star will form in a halo which contains a median number of four Pop III stars, with some containing as many as 16 Pop III stars. On the right, the red line indicates the median number of Pop III stars in each halo mass bin.}
\end{figure*}

@@
